### 2022-03-16 satfol/satfol.tex
fixes

\authors{
    Joint work with\\
    Jasmin Blanchette,
    and Marijn J.H. Heule
}

@@

Specializing second-order quantifier elimination
\cite{go-1992-so-pred-elim,hjo-1996-scan}, Khasidashvili and Korovin
\cite{kk-2016-pe-fol} adapted variable elimination to preprocess first-order
problems, yielding a technique we call \emph{singular predicate elimination}. We
extend their work along two axes (Sect.~\ref{sec:satfol:predicate-elimination}): We
generalize E\'en and Biere's refinement to first-order logic, resulting in
\emph{defined predicate elimination}, and explain how both types of predicate
elimination can be used during the proof search as inprocessing.

>>>>

\authors{
    Joint work with\\
    Jasmin Blanchette
    and Marijn J.H. Heule
}

@@

\begin{sloppypar}
    Specializing second-order quantifier elimination
    \cite{go-1992-so-pred-elim,hjo-1996-scan}, Khasidashvili and Korovin~\cite{kk-2016-pe-fol} adapted variable elimination to preprocess first-order
    problems, yielding a technique we call \emph{singular predicate elimination}. We
    extend their work along two axes (Sect.~\ref{sec:satfol:predicate-elimination}): We
    generalize E\'en and Biere's refinement to first-order logic, resulting in
    \emph{defined predicate elimination}, and explain how both types of predicate
    elimination can be used during the proof search as inprocessing.    
\end{sloppypar}
